```{r}
library(plotly)
library(shiny)
library(shinydashboard)
library(Rglpk)
library(ROI.plugin.glpk)
library(ROI)
library(ROI.plugin.quadprog)
library(tidyverse)
library(quantmod)
library(PerformanceAnalytics)
library(PortfolioAnalytics)
library(timetk)
library(tibbletime)
library(xts)
library(zoo)
library(tidyquant)
library(glue)
library(quadprog)
library(rlang)
library(webshot)
library(knitr)
library(purrr)
library(highcharter)
library(widgetframe)
library(scales)
library(DT)
library(lubridate)
library(dplyr)
library(tidyr)
library(reshape2)
#install.packages("foreach")
#install.packages("doParallel")
library(foreach)
library(doParallel)
library(tibble)
#install.packages("tseries")
#install.packages("DEoptim")
library(tseries)
library(plotly)
library(DEoptim)
library(tseries)
```


```{r}
start_date <- as.Date("2007-02-28")
end_date <- as.Date("2025-02-28")
symbols <- c("AAPL", "MSFT", "NVDA", "GOOGL", "AMZN", "META", "TSLA", "ORCL", "CRM", "ADBE")
```


```{r}
prices <- getSymbols(symbols, 
                     src = 'yahoo', 
                     from = start_date, 
                     to = end_date, 
                     auto.assign = TRUE, 
                     warnings = FALSE) |>
                    map(.f = ~Ad(get(x = .))) |> 
                    reduce(.f = merge) |> 
                    `colnames<-` (value=symbols)

```


```{r}
individual_monthly_returns <- to.monthly(
  x = prices,
  drop.time = TRUE,
  indexAt = "lastof",
  OHLC = FALSE
) |> 
  Return.calculate(method = 'discrete') |> 
  na.omit() |> 
  as.data.frame()
```

```{r}
individual_annualized_mean_returns <- individual_monthly_returns |> 
  summarise(across(everything(), mean, na.rm = TRUE)) |>
  mutate(across(everything(), ~ (. + 1)^12 - 1)) |>
  pivot_longer(cols = everything(), names_to = "Symbols", values_to = "Annualized Return")
individual_annualized_mean_returns
```

```{r}
individual_annualized_standard_deviations <- individual_monthly_returns |> 
  summarise(across(everything(), sd, na.rm = TRUE)) |>
  mutate(across(everything(), ~ . * sqrt(12))) |> 
  pivot_longer(cols = everything(), names_to = 'Symbols', values_to = 'Annual StdDev')
individual_annualized_standard_deviations
```
```{r}
assets_df <- inner_join(individual_annualized_mean_returns, individual_annualized_standard_deviations) |> 
  filter(Symbols != "NVDA")
assets_df
```



```{r}
# create max risk adjusted return portfolio 
portfolio <- portfolio.spec(assets = colnames(returns))

portfolio <- portfolio.spec(assets = colnames(returns))
portfolio <- add.constraint(portfolio, type = "full_investment")
portfolio <- add.constraint(portfolio, type = "box", min = 0, max = 1)
portfolio <- add.constraint(portfolio, type = 'long_only')
portfolio <- add.objective(portfolio, type = "return", name = "mean")
portfolio <- add.objective(portfolio, type = "risk", name = "var")


risk_adjusted_optimize_portfolio <- optimize.portfolio(returns, portfolio, optimize_method = "ROI", maxSR = TRUE,  trace = TRUE)
```

```{r}
risk_adjusted_optimize_portfolio
```

```{r}
risk_free_rate <- 0.05
annualized_risk_adjusted_return <- (1+risk_adjusted_optimize_portfolio$objective_measures$mean)^12 - 1
annualized_risk_adjusted_standard_deviation <- (risk_adjusted_optimize_portfolio$objective_measures$StdDev) * sqrt(12)
risk_adjusted_sharpe_ratio <- (annualized_risk_adjusted_arithmetic - risk_free_rate) / annualized_risk_adjusted_standard_deviation
```




```{r}
risk_adjusted_weights <- extractWeights(risk_adjusted_optimize_portfolio, 'weights')
```



```{r}
risk_adjusted_portfolio_returns <- Return.portfolio(R= returns,
                     weights = pluck(risk_adjusted_optimize_portfolio, 'weights'),
                     rebalance_on = "months",
                     geometric = TRUE
                     ) |> 
      `colnames<-`('risk_adjusted_portfolio_returns')
```



```{r}
annual_risk_adjusted_expected_return <- Return.annualized(risk_adjusted_portfolio_returns)

annual_risk_adjusted_StdDev <- StdDev(risk_adjusted_portfolio_returns) * sqrt(12)
```

```{r}
portfolio <- portfolio.spec(assets = colnames(returns))

portfolio <- portfolio.spec(assets = colnames(returns))
portfolio <- add.constraint(portfolio, type = "full_investment")
portfolio <- add.constraint(portfolio, type = 'long_only')
portfolio <- add.constraint(portfolio, type = "box", min = 0, max = 1)
portfolio <- add.objective(portfolio, type = "return", name = "mean")

max_return_optimize_portfolio <- optimize.portfolio(returns, portfolio, optimize_method = "Rglpk",  trace = TRUE)
```

```{r}
maximal_weights <- extractWeights(max_return_optimize_portfolio, 'weights')
maximal_weights
```
```{r}
risk_free_rate <- 0.05
annualized_max_return <- (1+max_return_optimize_portfolio$objective_measures$mean)^12 - 1
```

annualized_max_standard_deviation <- (max_return_optimize_portfolio$objective_measures$StdDev) * sqrt(12)
risk_adjusted_sharpe_ratio <- (annualized_risk_adjusted_arithmetic - risk_free_rate) / annualized_risk_adjusted_standard_deviation


```{r}
max_return_portfolio_returns <- Return.portfolio(
  returns,
  pluck(max_return_optimize_portfolio, 'weights'),
  rebalance_on = "months",
  geometric = TRUE
) |> 
  `colnames<-`('max_return_portfolio_returns')
```



```{r}
annual_max_expected_return <- Return.annualized(max_return_portfolio_returns)

annual_max_return_StdDev <-
  StdDev(max_return_portfolio_returns) * sqrt(12)
```

```{r}
portfolio <- portfolio.spec(assets = colnames(returns))

portfolio <- portfolio.spec(assets = colnames(returns))
portfolio <- add.constraint(portfolio, type = "full_investment")
portfolio <- add.constraint(portfolio, type = "box", min = 0, max = 1)
portfolio <- add.objective(portfolio, type = "risk", name = "var")

min_risk_optimize_portfolio <- optimize.portfolio(returns, portfolio, optimize_method = "quadprog",  trace = TRUE)
```


```{r}
min_var_weights <- extractWeights(min_risk_optimize_portfolio, "weights")
min_var_weights
```

```{r}
risk_free_rate <- 0.05
annualized_min_var_standard_deviation <- (min_risk_optimize_portfolio$objective_measures$StdDev) * sqrt(12)
```



```{r}
min_risk_portfolio_returns <- Return.portfolio(
  returns,
  pluck(min_risk_optimize_portfolio, 'weights'),
  rebalance_on = "months",
  geometric = TRUE
) |> 
  `colnames<-`('min_risk_portfolio_returns')
```


```{r}
annual_min_risk_expected_return <- Return.annualized(min_risk_portfolio_returns)

annual_min_risk_StdDev <-
  StdDev(min_risk_portfolio_returns) * sqrt(12)
```


```{r}
efficient_frontier <- extractEfficientFrontier(
  risk_adjusted_optimize_portfolio,
  match.col = "StdDev",
  n.portfolios = 100
                         )
```


```{r}
efficient_frontier$frontier
```

```{r}

cl <- makeCluster(detectCores() - 1)

mean_return <- efficient_frontier$frontier[, 1]
std_dev <- efficient_frontier$frontier[, 2]
weights <- efficient_frontier$frontier[, 4:13]

n.portfolios <- 100

annual_return <- (1 + mean_return) ^ 12 - 1
annual_std_dev <- std_dev * sqrt(12)
risk_free_rate <- 0.05
sharpe_ratio <- (annual_return - risk_free_rate) / annual_std_dev

weights_str <- apply(weights, 1, function(row) {
  paste(names(row), ":", round(row, 2), collapse = "<br>")
})

data_list <- sapply(1:length(mean_return), function(i) {
  list(x = std_dev[i], y = mean_return[i], weights = weights_str[i])
})

stopCluster(cl)
```


```{r}
annual_min_risk_expected_return
```

```{r}
optimal_sharpe <- risk_adjusted_sharpe_ratio
cml_x <- c(0, max(annual_std_dev))
cml_y <- risk_free_rate + optimal_sharpe * cml_x
```




```{r}
# Create the plot using plotly
plot_ly(
  x = ~annual_std_dev,
  y = ~annual_return,
  type = 'scatter',
  mode = 'markers+lines',
  text = ~paste("Risk (StdDev):", round(annual_std_dev, 2), 
                "<br>Return (Mean):", round(annual_return, 2),
                "<br>Sharpe Ratio:", round(sharpe_ratio, 2),
                "<br>Weights:<br>", weights_str),
  hoverinfo = 'text',
  marker = list(color = 'blue'),
  name = 'Efficient Frontier'
) |> 
  # Add the optimal portfolio point
  add_trace(
    x = annualized_risk_adjusted_standard_deviation,
    y = annualized_risk_adjusted_return,
    type = 'scatter',
    mode = 'markers',
    marker = list(color = 'red', size = 10),
    name = 'Optimal Portfolio',
    text = paste("Risk (StdDev):", round(annualized_risk_adjusted_standard_deviation, 4), 
                 "<br>Return (Mean):", round(annualized_risk_adjusted_return, 4),
                 "<br>Sharpe Ratio:", round(risk_adjusted_sharpe_ratio, 2),
                 "<br>Optimal Weights:<br>", paste(names(risk_adjusted_weights), ":", round(risk_adjusted_weights, 2), collapse = "<br>")),
    hoverinfo = 'text'
  ) %>%
  # Add the maximal portfolio point
  add_trace(
    x = annual_max_return_StdDev,
    y = annualized_max_return,
    type = 'scatter',
    mode = 'markers',
    marker = list(color = 'green', size = 10),
    name = 'Maximal Portfolio',
    text = paste("Risk (StdDev):", round(annual_max_return_StdDev, 2), 
                 "<br>Return (Mean):", round(annualized_max_return, 2),
                 "<br>Maximal Weights:<br>", paste(names(maximal_weights), ":", round(maximal_weights, 2), collapse = "<br>")),
    hoverinfo = 'text'
  ) %>%
  # Add the minimum variance portfolio point
  add_trace(
    x = annualized_min_var_standard_deviation,
    y = 0.22,
    type = 'scatter',
    mode = 'markers',
    marker = list(color = 'purple', size = 10),
    name = 'Minimum Variance Portfolio',
    text = paste("Risk (StdDev):", round(annualized_min_var_standard_deviation, 4), 
                 "<br>Return (Mean):", round(0.22, 4),
                 "<br>Minimum Variance Weights:<br>", paste(names(min_var_weights), ":", round(min_var_weights, 2), collapse = "<br>")),
    hoverinfo = 'text'
  )  |> 
  add_trace(
    x = cml_x,
    y = cml_y,
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'green', dash = 'dash'),
    name = 'Capital Market Line',
    text = 'Capital Market Line (CML)',
    hoverinfo = 'text'
  ) |> 
  
  add_trace(
    x = assets_df$`Annual StdDev`,
    y = assets_df$`Annualized Return`,
    type = 'scatter',
    mode = 'markers',
    marker = list(size = 8, color = 'orange'),
    name = 'Inferior Portfolios',
    text = ~paste("Asset:", assets_df$Symbols, 
                  "<br>Risk (StdDev):", round(assets_df$`Annual StdDev`, 2), 
                  "<br>Return (Mean):", round(assets_df$`Annualized Return`, 2)),
    hoverinfo = 'text'
  ) |> 
  layout(
    title = 'Annualized Efficient Frontier with Portfolios',
    xaxis = list(
      title = 'Risk (Portfolio Standard Deviation)',
      tickformat = ".2%",  # Format as percentage with 2 decimal places
      tickvals = seq(0, 0.8, by = 0.05)  # Custom tick values at intervals of 0.05
    ),
    yaxis = list(
      title = 'Portfolio Expected Return',
      tickformat = ".2%",  # Format as percentage with 2 decimal places
      tickvals = seq(0, 0.6, by = 0.05)  # Custom tick values at intervals of 0.05
    ),
    hoverlabel = list(
      bgcolor = "white",
      bordercolor = "black",
      font = list(color = "black")
    )
  )
```


