

```{r}
# install.packages("ROI")
# install.packages("ROI.plugin.quadprog")
# install.packages("Rglpk")
# install.packages("ROI.plugin.Rglpk")
# install.packages('webshot')
# install.packages('highcharter')
# install.packages('widgetframe')
#install.packages("quadprog")
#install.packages("shinydashboard")
library(Rglpk)
library(ROI.plugin.glpk)
library(ROI)
library(ROI.plugin.quadprog)
library(tidyverse)
library(quantmod)
library(PerformanceAnalytics)
library(PortfolioAnalytics)
library(timetk)
library(tibbletime)
library(xts)
library(zoo)
library(tidyquant)
library(glue)
library(quadprog)
library(rlang)
library(webshot)
library(knitr)
library(purrr)
library(highcharter)
library(widgetframe)
```


*Import daily prices from yahoo finance*'
*Data will be in the form of xts object, which is time series.*
*We are not specifying a start or end date to ensure we get the maximum, free data we can*


*using exchanged traded funds to analyze sector performance*



```{r}
symbols <- c('IXC', 'IXG', 'IXN', 'IXJ', 'IXP','RXI','EXI','MXI','KXI','JXI')

#I'm using getSymbols from quantmod library because it returns a time series object in xts form. 

prices <- getSymbols(
  Symbols = symbols,
  src = 'yahoo',
  auto.assign = TRUE,
  warnings = FALSE
) |> 
  # get() unpacks our financial price data (Open, High, Low, Close, Volume, Adjusted). Ad returns ONLY the daily adjusted price (accounts for any dividends paid, corporate actions, or adjustments that would effect the price of the stock. Map returns each individual stock data into a list. 
  map(.f = ~Ad(get(x = .))) |> 
  #reduce applies a function to each element of the list? 
  reduce(.f = merge) |> 
  # I needed to set the ticker symbol to the name of the columns. I found this nifty way of doing it since colnames(x=prices) <- value didn't work and I don't know why. Apparently this is prefix form. (Ex. AAPL.Adjusted is now AAPL)
  `colnames<-` (value=symbols)
prices
```


```{r}
monthly_adjusted_log_returns <- to.monthly(
x = prices,
drop.time = TRUE,
indexAt  = 'lastof',
OHLC = FALSE
 ) |> 
#compute our log returns
Return.calculate(
method = 'log') |> 
na.omit()
monthly_adjusted_log_returns
```



```{r}
#line charts of monthly log returns 
highchart(type = 'stock') |>
#   # Add chart main title
hc_title(text = "Monthly Log Returns") |> 
hc_add_series(
data = monthly_adjusted_log_returns[ , symbols[[1]]],
name = symbols[[1]]
) |> 
hc_add_series(
data = monthly_adjusted_log_returns[, symbols[[4]]],
name = symbols[[4]]
) |> 
hc_add_series(
data = monthly_adjusted_log_returns[, symbols[[3]]],
name = symbols[[3]]
) |> 
hc_add_theme(hc_thm = hc_theme_economist()) |> 
hc_exporting(enabled = TRUE) |> 
hc_legend(enabled = TRUE)
  
```

```{r}
 monthly_adjusted_log_returns_tibble <- monthly_adjusted_log_returns |> 
   tk_tbl() |> 
   rename(date = index) |> 
   pivot_longer(
     -date,
     names_to = 'Asset',
     values_to = 'Log_Returns'
   )
monthly_adjusted_log_returns_tibble
```


```{r}
 ggplot(
   monthly_adjusted_log_returns_tibble, mapping = aes(x=Log_Returns) +
     geom_histogram(
       alpha = 0.5,
       mapping = aes(fill= Asset)
     ) +
     ggtitle("Distributions of Monthly Log")
 )
```

```{r}
 # Compute Freedman-Diaconis bin numbers
 
 bins_fd <- function(vec) {
   ceiling(diff(range(vec)) / (2 * IQR(vec) / length(vec)^(1 / 3)))
 }
 # Histogram
 ggplot(monthly_adjusted_log_returns_tibble, mapping = aes(x = Log_Returns)) +
   geom_histogram(
     alpha = 0.5,
     mapping = aes(fill = Asset),
     bins = bins_fd(monthly_adjusted_log_returns_tibble[["Log_Returns"]])
   ) +
   facet_wrap(~Asset) + 
   ggtitle("Distributions of Monthly Log Returns") +
   theme_minimal()
```



```{r}
# # Density plot
 ggplot(data = monthly_adjusted_log_returns_tibble, mapping = aes(x = Log_Returns)) +
   geom_density(mapping = aes(color = Asset)) +
   ggtitle("Distributions of Monthly Log Returns") +
   theme(
     panel.background = element_rect(fill = "grey97"),
     panel.grid = element_blank()
   )
```

```{r}
 ggplot(data = monthly_adjusted_log_returns_tibble, mapping = aes(x = Log_Returns)) +
   geom_density(mapping = aes(color = Asset)) +
   geom_histogram(
     alpha = 0.5,
     mapping = aes(fill = Asset),
     bins = bins_fd(monthly_adjusted_log_returns_tibble[["Log_Returns"]])
   ) +
   facet_wrap(~Asset) +
   ggtitle("Distributions of Monthly Log Returns") +
   theme(
    panel.background = element_rect(fill = "grey97"),
     panel.grid = element_blank(),
   )
```


Variables: 
Rt = Return for a given period of time; 
Pt: Price at the end of period of time; 
Pt-1 = Price at the end of the previous period. 

Chaining Methods:
*Discrete (Arithmetic/Simple) Returns:
 formula: Rt = (Pt - (Pt-1)) / (Pt-1)
 Description: Computes percentage change from one period to the next. Often sued for short term analysis. Best used for daily or weekly price movements and trends. Doesn't account for compounding. linear. 
 
*Log returns
  formula: Rt = ln(Pt/Pt-1)
  description: computes percentage change from one period to the next. Versatile term analysis, so either daily, weekly, or monthly. Takes into consideration compounded growth for more accurate analysis. Applicable to statistical modeling. 



```{r}
# Keep only the last adjusted price of each month because we are focused on a long-term investment horizon, plus daily price flucuations cause too much noise can make it harder to identify long term trends. 

# to.monthly() function is apart of xts library and is used to convert daily price data to monthly. We have set the adjusted close price to the last of each month, dropped the time, and set OHLC = False which means no "OPEN, HIGH, LOW, CLOSE" values. 

monthly_adjusted_returns <- to.monthly(
  x = prices,
  drop.time = TRUE,
  indexAt = 'lastof', 
  OHLC = FALSE
) |> 
  #We calculating simple returns  with the return.calculate function from PerformanceAnalytics library
  Return.calculate(method = 'discrete') |> 
  na.omit()
```

```{r}
head(monthly_adjusted_returns)
```

```{r}
#Creates a portfolio object using portfolio.spec function, which is a function from of PortfolioAnalytics
# returns a list. 
Minimum_Variance_Portfolio <- portfolio.spec(assets = symbols)
Minimum_Variance_Portfolio
```

```{r}
# Add Full Investment Constraint (weight sum constraint - weights must sum to 1 - prevents overleveraging and ensures diversification)
Minimum_Variance_Portfolio <- add.constraint(
  portfolio = Minimum_Variance_Portfolio,
  type = 'weight_sum',
  min_sum = 0.99,
  max_sum = 1.01,
  enabled = TRUE
)
Minimum_Variance_Portfolio
```

```{r}
# Add Box Constraint(weights have minimum and maximum values - limits the range of weights in the portfolio. Limits over/under leveraging for assets. Promotes diversification)
Minimum_Variance_Portfolio <- add.constraint(
  portfolio = Minimum_Variance_Portfolio,
  type = 'box',
  min = 0,
  max = 1
)
Minimum_Variance_Portfolio
```

```{r}
# Add Objective to minimize risk (we are creating a minimization portfolio)
Minimum_Variance_Portfolio <- add.objective(
  portfolio = Minimum_Variance_Portfolio,
  type = 'risk',
  name = 'var'
)
Minimum_Variance_Portfolio
```

```{r}
Minimum_Variance_Portfolio <- optimize.portfolio(
  R = monthly_adjusted_returns,
  portfolio = Minimum_Variance_Portfolio,
  optimize_method = 'quadprog', 
  trace = TRUE
)
Minimum_Variance_Portfolio
```

```{r}
main_variance_portfolio_weights <- pluck(Minimum_Variance_Portfolio, 'weights')
main_variance_portfolio_weights
```
```{r}
tibble(
  asset = names(Minimum_Variance_Portfolio),
  allocation = Minimum_Variance_Portfolio
)
```



```{r}
monthly_StdDev <- (Main_Variance_Portfolio$objective_measures$StdDev)
annualized_StdDev <- (Main_Variance_Portfolio$objective_measures$StdDev*sqrt(12))
glue("Your Monthly Standard Deviation is {monthly_StdDev}")
glue("Your Annualized Standard Deviation is {annualized_StdDev}")
```

```{r}
Minimized_Portfolio_Returns <- Return.portfolio(
  R = monthly_adjusted_returns,
  weights = main_variance_portfolio_weights,
  #aggregate monthly 
  rebalance_on = "months",
  geometric = FALSE
) |> 
  `colnames<-`("Monthly_portfolio_returns")
Minimized_Portfolio_Returns
```



*creating Maximal Return expected Portfolio*



```{r}
#Creates a portfolio object using portfolio.spec function, which is a function from of PortfolioAnalytics
# returns a list. 

maximum_expected_return_portfolio <- portfolio.spec(
  assets = symbols
)
maximum_expected_return_portfolio
```

```{r}
# Add weight_sum Constraint (weight sum constraint)

maximum_expected_return_portfolio <- add.constraint(
  portfolio = maximum_expected_return_portfolio,
  # similar to full_investment, expect you can modify the parameters for 'min_sum' and 'max_sum' to ease up constraints for calculating maximal returns
  type = 'weight_sum',
  min_sum = 0.99,
  max_sum = 1.01,
  enabled = TRUE
)
maximum_expected_return_portfolio
```


```{r}
# Adding box constraint
maximum_expected_return_portfolio <- add.constraint(
  portfolio = maximum_expected_return_portfolio,
  type = 'box',
  min = 0.1,
  max = 0.6
)
maximum_expected_return_portfolio
```

```{r}
# Add objective function - we are implementing a linear function to calculate the maximal expected returns 
maximum_expected_return_portfolio <- add.objective(
  portfolio = maximum_expected_return_portfolio,
  type = 'return',
  # name of function used to calculate the returns (we're just naming the type = 'return' parameter.:
  name = 'mean'
)
maximum_expected_return_portfolio
```

```{r}
# Optimize the portfolio
main_expected_return_portfolio <- optimize.portfolio(
  R = monthly_adjusted_returns,
  portfolio = maximum_expected_return_portfolio,
  # used for linear functions with linear constraints
  optimize_method = "Rglpk",
  trace = TRUE
)
main_expected_return_portfolio
```

```{r}
main_expected_return_portfolio_weights <- pluck(main_expected_return_portfolio,
      'weights'
)
main_expected_return_portfolio_weights
```




```{r}
#average annual return you can expect to earn. 
monthly_Return <- (main_expected_return_portfolio$objective_measures$mean)
annualized_Return <- (1+main_expected_return_portfolio$objective_measures$mean)^12-1
glue("Your maximal expected monthly return is {monthly_Return}")
glue("Your maximal annualized expected return is {annualized_Return}")
```

```{r}
# We are using the Return.portfolio() function from Performance Analytics to calculate the percentage returns per month. It's based on the weights for the asset and the assets return that month. 
Return.portfolio(
  R = monthly_adjusted_returns,
  weights = main_expected_return_portfolio_weights,
  #aggregate monthly 
  rebalance_on = "months",
  geometric = FALSE
) |> 
  `colnames<-`("Monthly_portfolio_returns")
```

*Return the tangent portfolio*


we are trying to find the combination of asset weights that yield the highest risk-adjusted return:
* maximize the numerator (expected return - risk-free rate)
* minimize the denominator (the portfolio standard deviation)


```{r}
tangent_portfolio <- portfolio.spec(assets = symbols)
tangent_portfolio
```

```{r}
tangent_portfolio <- add.constraint(
  portfolio = tangent_portfolio,
  type = "weight_sum",
  min = 0.99,
  max = 1.01
)
```


```{r}
tangent_portfolio <- add.constraint(
  portfolio = tangent_portfolio,
  type = "box",
  min = 0,
  max = 1
)

```


# Setting the Sharpe Ratio as an objective. The optimizer "ROI" will seek to maximize the sharpe ratio which plays a pivotal role in calculating the optimal weights in a portfolio by considering both the expected return and the risk. When optimizing for the Sharpe Ratio, the goal is to find the combination of asset weights that provides the highest risk-adjusted return.
```{r}
tangent_portfolio <- add.objective(
  portfolio = tangent_portfolio,
  type = 'risk_adjusted_return',
  name = 'SharpeRatio',
  risk_free_rate = 0.005
)
```

The sharpe ratio incorporates the expected return, guiding the optimizer to choose assets with higher returns. 

```{r}
main_tangent_portfolio <- optimize.portfolio(
  R = monthly_adjusted_returns,
  portfolio = tangent_portfolio,
  optimize_method = "ROI",
  trace = TRUE
)
main_tangent_portfolio
```



```{r}
Optimal_Return_monthly <- (main_tangent_portfolio$objective_measures$mean)
annualized_Return_monthly <- (1+main_tangent_portfolio$objective_measures$mean)^12-1

glue("Your optimal return monthly return is {monthly_Return}")
glue("Your optimal annualized return is {annualized_Return}")
```

```{r}
main_tangent_portfolio_weights <- pluck(main_tangent_portfolio,
      'weights'
)

main_tangent_portfolio_weights
```



```{r}
tangent_portfolio_return <- Return.portfolio(
  R = monthly_adjusted_returns,
  weights = main_tangent_portfolio_weights,
  #aggregate monthly 
  rebalance_on = "months",
  geometric = FALSE
) |> 
  `colnames<-`("Monthly_portfolio_returns")

tangent_portfolio_return
```



